Regime transition identification for basin's governance challenges of water use

### 2020-11-18 tex/main/manuscript.tex
update polish

\begin{figure*}%[htbp]
	\centering
	\includegraphics[width=0.8\linewidth]{../../figures/main/framework.jpg}
	\caption{
		A schematic diagram for understanding the changing relationship between social development and water governance.
		% 图A是水资源利用的三个维度。每个维度都有两个极点（红色字表示），指示水资源利用在该轴上的两个变化方向。
		\textbf{A,} three dimensions (stress, provision and allocation) of water resources governance. Each dimension has two poles (denoted in red) which indicates the two potential directions of water resources governance changes along that axis. (1) Stress of water governance shifts between scarcity of water resources and abundance of water resources, which means there is shortage of water supply or not. (2) provision of water governance can move between a provisioning part or a non-provisioning one, indicating how much water were used in food supporting to human societies. (3) allocation can move between balanced or lopsided, when allocation of water resources between different sectors or regions changed. We presume that water governance regimes equally weighted by these basic dimensions, whose combination can highly relate to basin development. 
		% 图B是将三个维度结合后的变化情况。因上述三个维度随着社会发展而不断变化，其组合的水资源利用状态也不同。这个过程中当突变发生时，可能标志着水资源利用发生了稳态转换，因此我们需要一个指标来监测其变化。
		\textbf{B,} the changes after combining the three dimensions. Because the above three dimensions are changing with the development of society, their combined water resource governance status is also different. When abrupt transitions occur during this process, they may indicate a regime shift in water governance, so we need an indicator to monitor this change.
	}
	\label{fig:framework}
\end{figure*}

@@

\begin{figure}[ht!]
	\centering
	\includegraphics[width=\linewidth]{../../figures/main/index.pdf}
	\caption{Changes of the IWGI index. 
	\textbf{A,} Change points detection. With change points in 1978 and 1994, the IWGI have three periods in changing trend.
	\textbf{B,} Changing slopes of each period.
	\textbf{C,} Contributions of each dimension to the changes of IWGI within three periods. Stress, provision and allocation are the main positive contributor of P1, P2 and P3, respectively.
	}
	\label{fig:IWGI}
\end{figure}

% 这一节主要展示IWGI的变化趋势和WUR的划分
With two significant points, the changing trend of IWGI index are detected into three periods (Figure~\ref{fig:IWGI}A). 
Not only the slope of changes are various within each period, changes are also mainly contributed by different dimensions (Figure~\ref{fig:IWGI}B and Figure~\ref{fig:IWGI}C).
% 第一阶段
In the first period (P1, 1965-1978), the IWGI index had a rapidly increasing and the lightening of water stresses made the most striking positive contribution (131\%), while provision and allocation of the water governance had slight negative contribution (-11\% and -20\%).
% 第二阶段
In the second period (P2, 1979-1994), though contributions of provision and allocation turned into positive, the IWGI index experienced a drop because of stresses on water resource playing a larger negative role (-188\% dropped than P1). 
% 第三阶段
However, as the further increasing of positive contributions of provision (75\%) and allocation (84\%), and decreases of water stresses in negative contribution (-59\%) in the third period (P3, 1995-2013), a positive growth of the IWGI returned.

\begin{figure}[!htbp]
	\centering
	\includegraphics[width=0.9\linewidth]{../../figures/main/phases.pdf}
	\caption{Combination of contributions regards three dimensions in different periods (S: stresses; P: provision; C: allocation). The closer a point to an angle of the triangle, greater the proportion of the contribution of this dimension.
	The red indicator line in this ternary plot denotes 1:1 contributions between provision (P) and allocation (C). When the points are bellow this line, the contribution ratio of allocation is lower than that of provision, and vice versa.}
	% 由于阶段一的点位于该线上方，L的净贡献比例多于P，而第二阶段的点则恰好相反。
	\label{fig:phases}
\end{figure}

% 总而言之，每个阶段都由水资源利用的不同维度提供最大的正向作用
Taken together, each period has the unique most striking positive contributor to IWGI, and overall features of three dimensions in different periods are shown in Figure~\ref{fig:phases}.
% 第一阶段到第二阶段
At the very beginning (1965) and throughout the whole P1, water governance regime dominated by lower stresses. After then, it experienced a shift to high stresses since 1978, with a change in the proportion of contributions between provision and allocation, too.
% 第三阶段集中
Finally, the contribution of three dimensions were much similar in P3 (32.91\%, 31.87\% and 35.21\% for provision, allocation and stress respectively), making the points highly concentrated at the centre of the ternary diagram in that period.

@@

\begin{figure}[th!]
	\centering
	\includegraphics[width=\linewidth]{../../figures/main/causes.pdf}
	\caption{
		Drivers of water governance regime shifts: economy growths, efficiency changes, and management practices.
		\textbf{A.} Changes of total irrigated area, and water consumptions in per unit of area (\textit{SI Method} S2).
		\textbf{B.} Changes of gross values added (GVA) of industry and services, and their water use density (WUI) respectively (\textit{SI Appendix} Method S2).
		\textbf{C.} Completed time of each new reservoir and their located regions' water use percentages in basin's total water use (WU), at that time. Red ones denote hub reservoirs in the basin, which plays a role in basinal integrated water management. Size of the points indicates their magnitude of water storage capacities. Some important or special reservoirs' name denoted: (1) Xiaolangdi reservoir and Sanmen Reservoir were constructed mainly responsible for managing sediments of the Yellow River. (2) Liujia Gorge, Longyang Gorge, were constructed mainly responsible for managing water flood discharge and storage. These marked reservoirs, therefore are significant for the entire basin, far crucial than regional development.
	}
	\label{fig:Causes}
\end{figure}

% 经济总量提升导致资源耗竭的加速。
Firstly, the expansion of irrigated area and the economic growth of industry and services are keys to the changes in the provision of water use between P1 and P2 (Figure\ref{fig:Causes}A). During the P1, irrigated agricultural area in the Yellow River basin expanded rapidly at a rate of $0.25*10^6 ha/yr$, and irrigation water was the dominant governance way ($81.56\%$ of the total water use in 1965, and $83.17\%$ in 1978, see \textit{SI Appendix} Fig. S7). Entering P2, however, while the expansion of irrigated area stalled, industry and services gradually took off and took up more water resources (Figure\ref{fig:Causes} B), leading to $8\%$ reduction of proportion of irrigation water (\textit{SI Appendix} S7).

% 用水关系的变化
Secondly, efficiency of water use changed from the P2 to the P3.
While irrigated area resumed expansion again in the P3 whose water consumptions were still dominant (Figure\ref{fig:Causes}A), both industry, urban services were boosting their gross added values (GVA) (Figure~\ref{fig:Causes}B). 
However, the water use density (WUI) of them experienced significant declines and reached the lowest points (Figure~\ref{fig:Causes}A and Figure~\ref{fig:Causes}B).
It means, water governance ways  have changed, along with technological solutions and a range of water conservation practices (\textit{SI Appendix} Fig. S8). As a result, the differences between the sectors of water use reduced while the total water consumption remains stable, during the P3 (\textit{SI Appendix} Fig. S7).

% 不断变化的管理模式。
Finally, water policies and management practices contributed throughout all three periods. 
According to the location, we calculate the ratios of regional and basinal water use for each reservoir.
In the P1, most of the reservoirs are built in regions with high water demands, as ratios are significantly higher (Figure~\ref{fig:Causes}C, p<0.01). 
In the P2, the number of new reservoirs decreases significantly with little increment of total storage capacities (\textit{SI Appendix} Fig. S6). 
Entering the P3, however, the number of new reservoirs are even much higher than that in the P1, and most of them were built in regions with lower ratio of regional water use (Figure~\ref{fig:Causes}C and \textit{SI Appendix} Fig. S6).

@@

\begin{figure*}[htbp!]
	\centering
	\includegraphics[width=\linewidth]{../../figures/main/transition.jpg}
	\caption{
		\textbf{Transition framework of water governance.} Blue pathways dominated by natural water loop while red ones dominated by socio-economic loops. 
		\textbf{A. Natural phase:} As an indispensable provisioning resource, the main functions of water resource is to support crop, livestocks and human-beings, which are the basic ecological services.
		\textbf{B. Local phase:} With local socio-economic systems developing, industry and services (also known as the secondary and the tertiary industry) calling for further water consumptions. What's more, better organized socio-economic system and developed technology gives humans abilities in better managing water resources, with intensive intervention in the natural water cycle. 
		\textbf{C. Regional phase:} With further developed and economically efficient industries and services, trade-off between whose water demands with provisional water demands becomes prominent. Rather than determined by local socio-economic systems, water withdrawals and management act as considerations within the entire basin more, therefore. 
	}
	\label{fig:summary}
\end{figure*}

% 我们发明的指数能同时关注水资源治理的三个关键方面。
The IWGI index we developed captures three key dimensions of water governance simultaneously: (water use stress, provision of water use and allocation for water use). 
% 我们为的研究结果表明，黄河流域能被识别为三个明显的稳态。
Based on that, our results show that three distinct but sequential governance regimes within YRB, whose shifts have been caused by different environmental, economic, social or political aspects.
% 值得注意的是，这些多方面的变化随着流域逐步迈向水-社会循环的过程中逐步发生的，且在早期主要带来经济、环境方面的挑战，而后期则带来社会和政策方面的挑战。
It is important to note that these regimes with multifaceted causes occurred gradually as the basin moves towards a hydro-social cycle, facing primarily economic and environmental challenges in the early stages while social and policy challenges in the later stages.

@@

% 第三次稳态转换直到1993年左右才由用水效率的显著提升而带来，因为社会经济发展后先进技术的广泛应用。
The next regime shift was not brought until a significant increase in water use efficiency around 1993, due to the widespread applying of advanced technologies after socio-economic developments. 
% 而区域社会经济的权衡成为了用水分配的关键，如此时期普及开的水权转换项目就是把节约的农业用水用于工业发展。
The regional socio-economic trade-off had become the key to water governance in this period, and for an example, the water rights conversion project popularized in this regime is to use the saved agricultural water for industrial developments.
% 但是曾帮助流域摆脱环境危机的分水政策却在此时期成为了流域协调和社会公平的桎梏。
However, the water allocating policy (i.g. ``87 Water Diversion Scheme''), which had helped the YRB get rid of the environmental crisis in the last regime, became the shackle of equity and coordination during this period.
% 这是因为用水分配方案高度路径依赖，用水方式也更加不灵活，这些成为新的社会经济形势下的治理难题。
This is because the water allocation scheme is highly path dependent and the way of water use is also more inflexible, both of which have become challenges for governance under the new regime.

% 总的来说，三个水治理稳态之间的先后转变，都是随着流域向社会-水循环发展的过程中先后发生的，存在明显的过渡趋势。
In general, shifts of the three governance regimes occurred sequentially with the transformation towards the hydro-social cycle, with an obvious transition.
% 随着不断增强的人类压力在全球普遍逐渐占据主导，这种过渡趋势在社会-生态系统中被认为是普遍存在的，例如生态系统服务和国家经济-社会发展。
This transition is considered to be pervasive in socio-ecological systems, such as ecosystem services and national economic-social developments, as increasing anthropogenic pressures gradually dominate the world at large.
% 流域转向社会-水循环的过程就是典型的社会-生态系统过渡过程，而我们发现在这一过程中水治理的稳态转换呼应了全球水治理面临的两大主要挑战。
With the typical transition towards a hydro-social water cycle, we find that the regime shifts of water governance echoes the two major challenges globally.
% 根据前人广泛的总结，目前全球一部分流域正面临着经济发展和资源困境（如缺水和用水困难），而另一些则迫切需要社会政策层面的协调与合作以实现可持续（如跨境河流的用水分配与协作治理）。
According to the summary of previous studies, some river basins are facing economic development and resource dilemma (such as water shortage and water supplying difficulties), while others are in urgent need of coordination and cooperation at the social policy (such as water disputes and lack of cooperative governance, especially for cross-border rivers).
% 非常具有代表性的是，这两类主要挑战在黄河流域快速变迁的过程中先后发生了，伴随着整合了四个维度的（经济、环境、社会、政策）治理稳态的转换。
It is very representative that these two kinds of major challenges have occurred successively in the transition of the YRB, accompanied by the transformation of governance regime.
% 我们的分析表明，过渡的前期常常带来环境和经济层面的治理挑战，而在过渡的后期则主要是社会和政策层面的挑战。
Our analysis indicates that the early stage of transition often brings environmental and economic governance challenges, while the later stage of transition is dominated by social and policy challenges.
% 再一次，我们总结的框架呼应了联合国发展属为水治理提出的四个维度和两大主要问题。
Again, our schema have outlined echoes the four dimensions (economic, environmental, social and political) summarized by UNDP, and two types of global challenges, regarding water governance.

@@

% 我们发展的指数捕捉了水治理的过渡制度，以一种相对全面但简单的方式
The index we developed (IWGI), captures the transition regimes of water governance with different challenges, in a relatively simple but comprehensive way.
% 对可持续科学家来说，认识到治理挑战的变化非常重要，因为发展不是解决一切的灵丹妙药。
It is important for scientists and decision makers to recognize the changing challenges for water governance, because development is not a panacea for all basin issues regarding sustainability.
% 对于当今世界来说，水资源供应压力不断增大仍然是全球最大的水治理挑战，而经济优先的策略仍然是应对挑战的主要方式。
For today's world, increasing water stresses on water use remains one of the greatest water governance challenges, while economic development provision strategies are still the main guideline to meet them. 
% 尽管绝大多数的大河流域都在快速发展的同时极大提高了管理水资源的能力和用水的效率，但大部分研究仍悲观的指出淡水利用已经临近系统崩溃的行星边界。
Although most large river basins improved water management and efficiency along with development, most studies still pessimistically point out that freshwater use is reaching planetary boundaries where human-water systems may collapse.
% 总的来说，这可能有两点主要原因。
Overall, there are probably two main reasons.
% 首先，效率悖论
Firstly, significant improvement in agricultural irrigation efficiency is usually accompanied by re-expansion in irrigated area, resulting in a usually unabated trend of water resources stress which is known as paradox of efficiency 
\cite{graftonParadoxIrrigationEfficiency2018}. 
% 其次，以水-社会水循环为主导的治理机制下，水资源分配或提供结构复杂，可能导致水资源利用不灵活，破坏流域的恢复能力
Secondly, complicated structure of water allocation or provision under a governance regime dominated by hydro-social water cycle may lead the water governance more inflexible and damage to resilience of the basin
\cite{qinFlexibilityIntensityGlobal2019}.
% 这时，我们需要相应的全面策略应对这种治理挑战，因为挑战的核心要素超出了任何一个参与的控制。
At this point, we need corresponding comprehensive strategies to address the governance challenges, because the heart factors of are beyond the control of any related actor. 
% 基于对治理稳态的认识，我们可以为应对挑战创造有利条件，让利益相关者实现对社会和环境状况的预期，从而维持流域社会-生态系统的弹性。
Based on the understanding of governance regime transition, we can create favourable conditions for meeting the challenges and enabling stakeholders to realize their expectations of social and environmental changes, thus maintaining the resilience of the basin's socio-ecosystem.
% 总的来说，这些都有助于指导流域迈向可持续性。
Taken together, these have helped guide the basin towards sustainability.

>>>>

\begin{figure*}%[htbp]
	\centering
	\includegraphics[width=0.8\linewidth]{../../figures/main/framework.jpg}
	\caption{
		A framework for understanding the relationship between transformation towards hydro-social cycle and water governance regimes.
		% 图A是水资源利用的三个维度。每个维度都有两个极点（红色字表示），指示水资源利用在该轴上的两个变化方向。
		\textbf{A,} three dimensions (storage, provision and allocation) of water governance (see \textit{Appendix SI} Methods S4 for details). Each dimension has two poles (denoted in red) which indicate the two potential directions of changes along that axis. (1) Storage shifts between scarcity of water resources and abundance of water resources, which means there is shortage of water supply or not. (2) provision of water can move between provisioning services or non-provisioning services, indicating how much water were used in food supporting. (3) allocation can move between balanced or lopsided, when allocation of water resources between different sectors or regions changed. We presume that water governance regimes equally weighted by these basic dimensions, whose combination can highly relate to basin development. 
		% 图B是将三个维度结合后的变化情况。因上述三个维度随着社会发展而不断变化，其组合的水资源利用状态也不同。这个过程中当突变发生时，可能标志着水资源利用发生了稳态转换，因此我们需要一个指标来监测其变化。
		\textbf{B,} the changes after combining the three dimensions. Because the above three dimensions are changing with the trajectory towards hydro-social water cycle, their combined water governance status is also different. When abrupt change occur during this process, they may indicate a regime shift in water governance, and we propose an indicator to monitor this change.
	}
	\label{fig:framework}
\end{figure*}

@@

\begin{figure}[ht!]
	\centering
	\includegraphics[width=\linewidth]{../../figures/main/index.pdf}
	\caption{Changes of the IWGI index. 
	\textbf{A,} Change points detection. With change points in 1978 and 1994, the IWGI have three periods in changing trend.
	\textbf{B,} Changing slopes of each period.
	\textbf{C,} Contributions of each dimension to the changes of IWGI within three periods. Storage, provision and allocation are the main positive contributor of P1, P2 and P3, respectively.
	}
	\label{fig:IWGI}
\end{figure}

% 这一节主要展示IWGI的变化趋势和WUR的划分
With two significant points, the changing trend of IWGI index are detected into three periods (Figure~\ref{fig:IWGI}A). 
Not only the slope of changes are various within each period, changes are also mainly contributed by different dimensions (Figure~\ref{fig:IWGI}B and Figure~\ref{fig:IWGI}C).
% 第一阶段
In the first period (P1, 1965-1978), the IWGI index had a rapidly increasing and the storage made the most striking positive contribution (131\%), while provision and allocation had slight negative contribution (-11\% and -20\%).
% 第二阶段
In the second period (P2, 1979-1994), though contributions of provision and allocation turned into positive, the IWGI index experienced a drop because declining storage plays a larger negative role (-188\% dropped than P1). 
% 第三阶段
However, as the further increasing of positive contributions of provision (75\%) and allocation (84\%), and decreases of water storage in negative contribution (-59\%) in the third period (P3, 1995-2013), a positive growth of the IWGI returned.

\begin{figure}[!htbp]
	\centering
	\includegraphics[width=0.9\linewidth]{../../figures/main/phases.pdf}
	\caption{Combination of contributions regards three dimensions in different periods (S: storage; P: provision; C: allocation). The closer a point to an angle of the triangle, greater the proportion of the contribution of this dimension.
	The red indicator line in this ternary plot denotes 1:1 contributions between provision (P) and allocation (C). When the points are bellow this line, the contribution ratio of allocation is lower than that of provision, and vice versa.}
	% 由于阶段一的点位于该线上方，L的净贡献比例多于P，而第二阶段的点则恰好相反。
	\label{fig:phases}
\end{figure}

% 总而言之，每个阶段都由水资源利用的不同维度提供最大的正向作用
Taken together, each period has the unique most striking positive contributor to IWGI, and overall features of three dimensions in different periods are shown in Figure~\ref{fig:phases}.
% 第一阶段到第二阶段
At the very beginning (1965) and throughout the whole P1, water governance regime dominated by increasing storage. After then, it experienced a shift to slow down in increasing storage since 1978, with a change in the proportion of contributions between provision and allocation, too.
% 第三阶段集中
Finally, the contribution of three dimensions were much similar in P3 (32.91\%, 31.87\% and 35.21\% for provision, allocation and storage respectively), making the points highly concentrated at the centre of the ternary diagram in that period.

@@

\begin{figure}[th!]
	\centering
	\includegraphics[width=\linewidth]{../../figures/main/causes.pdf}
	\caption{
		Causes of water governance regime shifts: environment changes, economic growths and efficiency changes, social transformation and water governance policies.
		\textbf{A.} Changes of total irrigated area, and water consumptions in per unit of area (\textit{SI Method} S2).
		\textbf{B.} Changes of gross values added (GVA) of industry and services, and their water use density (WUI) respectively (\textit{SI Appendix} Method S2).
		\textbf{C.} Completed time of each new reservoir and their located regions' water use percentages in basin's total water use (WU), at that time. Red ones denote hub reservoirs in the basin, which plays a role in basinal integrated water management. Size of the points indicates their magnitude of water storage capacities. Some important or special reservoirs' name denoted: (1) Xiaolangdi reservoir and Sanmen Reservoir were constructed mainly responsible for managing sediments of the Yellow River. (2) Liujia Gorge, Longyang Gorge, were constructed mainly responsible for managing water flood discharge and storage. These marked reservoirs, therefore are significant for the entire basin, far crucial than regional development.
	}
	\label{fig:Causes}
\end{figure}

% 经济总量提升导致资源耗竭的加速。
Firstly, the expansion of irrigated area and the economic growth of industry and services are keys to the changes in the provision between P1 and P2 (Figure\ref{fig:Causes}A). During the P1, irrigated agricultural area in the Yellow River basin expanded rapidly at a rate of $0.25*10^6 ha/yr$, and irrigation water was the dominant water use ($81.56\%$ of the total water use in 1965, and $83.17\%$ in 1978, see \textit{SI Appendix} Fig. S7). Entering P2, however, while the expansion of irrigated area stalled, industry and services gradually took off and took up more water resources (Figure\ref{fig:Causes} B), leading to $8\%$ reduction of proportion of irrigation water (\textit{SI Appendix} S7).

% 用水关系的变化
Secondly, efficiency of water use changed from the P2 to the P3.
While irrigated area resumed expansion again in the P3 whose water consumptions were still dominant (Figure\ref{fig:Causes} A), both industry, urban services were boosting their gross added values (GVA) (Figure~\ref{fig:Causes}B). 
However, the water use density (WUI) of them experienced significant declines and reached the lowest points (Figure~\ref{fig:Causes}A and Figure~\ref{fig:Causes}B).
It means, water governance have changed, along with technological solutions and a range of water conservation practices (\textit{SI Appendix} Fig. S8). As a result, the differences between the sectors of water use reduced while the total water consumption remains stable, during the P3 (\textit{SI Appendix} Fig. S7).

% 不断变化的管理模式。
Finally, environmental context, social transformation and water governance policies played roles throughout all three periods. 
According to the location, we calculate the ratios of regional and basinal water use for each reservoir.
In the P1 when natural water resource is relatively abundant (see \textit{SI Appendix} Figure S3), most of the reservoirs are built in regions with high water demands, as ratios are significantly higher (Figure~\ref{fig:Causes}C, p<0.01). 
In the P2, the number of new reservoirs decreases significantly with little increment of total storage capacities (\textit{SI Appendix} Fig. S6).  
Entering the P3, however, the number of new reservoirs are even much higher than that in the P1, and most of them were built in regions with lower ratio of regional water use (Figure~\ref{fig:Causes}C and \textit{SI Appendix} Fig. S6).
% After the major environmental regulation, myriad new water policies proposed during this period.

@@

\begin{figure*}[htbp!]
	\centering
	\includegraphics[width=\linewidth]{../../figures/main/transition.jpg}
	\caption{
		\textbf{Transition schema of water governance.} Blue pathways dominated by natural water loop while red ones dominated by socio-economic loops. There is a transformation towards the hydro-social water cycle where red loop increases.
		\textbf{A. Natural phase:} As an indispensable provisioning resource, the main functions of water resource is to support crop, livestocks and human-beings, which are the basic ecological services.
		\textbf{B. Local phase:} With local socio-economic systems developing, industry and services (also known as the secondary and the tertiary industry) calling for further water consumptions. What's more, better organized socio-economic system and developed technology gives humans abilities in better managing water resources, with intensive intervention in the natural water cycle. 
		\textbf{C. Regional phase:} With further developed and economically efficient industries and services, trade-off between whose water demands with provisional water demands becomes prominent. Rather than determined by local socio-economic systems, water withdrawals and management act as considerations within the entire basin more, therefore. 
		Water governance faces primarily economic and environmental challenges in the early stages while social and policy challenges in the later stages.
	}
	\label{fig:summary}
\end{figure*}

% 我们发明的指数能同时关注水资源治理的三个关键方面。
The IWGI index we developed captures three key dimensions of water governance simultaneously: (storage, provision and allocation). 
% 我们为的研究结果表明，黄河流域能被识别为三个明显的稳态。
Based on that, our results show that three distinct but sequential governance regimes within YRB, whose shifts have been caused by different environmental, economic, social or political aspects.
% 值得注意的是，这些多方面的变化随着流域逐步迈向水-社会循环的过程中逐步发生的，且在早期主要带来经济、环境方面的挑战，而后期则带来社会和政策方面的挑战。
It is important to note that these regimes with multifaceted causes occurred gradually as the basin moves towards a hydro-social cycle, facing primarily economic and environmental challenges in the early stages while social and policy challenges in the later stages (Figure~\ref{fig:summary}).

@@

% 第三次稳态转换直到1993年左右才由用水效率的显著提升而带来，因为社会经济发展后先进技术的广泛应用。
The next regime shift was not brought until a significant increase in water use efficiency around 1993, due to the widespread applying of advanced technologies after socio-economic developments. 
% 而区域社会经济的权衡成为了用水分配的关键，如此时期普及开的水权转换项目就是把节约的农业用水用于工业发展。
The regional socio-economic trade-off had become the key to water governance in this period, and for an example, the water rights conversion project popularized in this regime is to use the saved agricultural water for industrial developments.
% 但是曾帮助流域摆脱环境危机的分水政策却在此时期成为了流域协调和社会公平的桎梏。
However, the water allocating policy (i.g. ``87 Water Diversion Scheme''), which had helped the YRB get rid of the environmental crisis at the last regime, became the shackle of equity and coordination during this period.
% 这是因为用水分配方案高度路径依赖，用水方式也更加不灵活，这些成为新的社会经济形势下的治理难题。
This is because the water allocation scheme is highly path dependent and the way of water use is also more inflexible, both of which have become challenges for governance under the new regime.

% 总的来说，三个水治理稳态之间的先后转变，都是随着流域向社会-水循环发展的过程中先后发生的，存在明显的过渡趋势。
In general, shifts of the three governance regimes occurred sequentially with the transformation towards the hydro-social cycle, with an obvious transition.
% 随着不断增强的人类压力在全球普遍逐渐占据主导，这种过渡趋势在社会-生态系统中被认为是普遍存在的，例如生态系统服务和国家经济-社会发展。
This transition is considered to be pervasive in socio-ecological systems, such as ecosystem services and national economic-social developments, as increasing anthropogenic pressures gradually dominate the world at large.
% 流域转向社会-水循环的过程就是典型的社会-生态系统过渡过程，而我们发现在这一过程中水治理的稳态转换呼应了全球水治理面临的两大主要挑战。
With the typical transition towards a hydro-social water cycle, we find that the regime transition of water governance echoes the two kinds of major challenges globally.
% 根据前人广泛的总结，目前全球一部分流域正面临着经济发展和资源困境（如缺水和用水困难），而另一些则迫切需要社会政策层面的协调与合作以实现可持续（如跨境河流的用水分配与协作治理）。
According to the summary of previous studies, some river basins are facing economic development and resource dilemma (such as water shortage and water supplying difficulties), while others are in urgent need of coordination and cooperation at the social policy (such as water disputes and lack of cooperative governance, especially for cross-border rivers).
% 非常具有代表性的是，这两类主要挑战在黄河流域快速变迁的过程中先后发生了，伴随着整合了四个维度的（经济、环境、社会、政策）治理稳态的转换。
It is very representative that these two kinds of major challenges have occurred successively in the transition of the YRB, accompanied by the transformation of governance regime.
% 我们的分析表明，过渡的前期常常带来环境和经济层面的治理挑战，而在过渡的后期则主要是社会和政策层面的挑战。
Our analysis indicates that the early stage of transition often brings environmental and economic governance challenges, while the later stage of transition is dominated by social and policy challenges.
% 再一次，我们总结的框架呼应了联合国发展属为水治理提出的四个维度和两大主要问题。
Again, this schema outlines the key dimensions proposed by UNDP and two types of global challenges, regarding water governance.

@@

% 我们发展的指数捕捉了水治理的过渡制度，以一种相对全面但简单的方式
The index we developed (IWGI), captures the transition regimes of water governance with different challenges, in a relatively simple but comprehensive way.
% 对可持续科学家来说，认识到治理挑战的变化非常重要，因为发展不是解决一切的灵丹妙药。
It is important for scientists and decision makers to recognize the changing challenges for water governance, because development is not a panacea for all basin issues regarding sustainability.
% 对于当今世界来说，水资源供应压力不断增大仍然是全球最大的水治理挑战，而经济优先的策略仍然是应对挑战的主要方式。
For today's world, increasing water stresses on water use remains one of the greatest water governance challenges, while economic development provision strategies are still the main guideline to meet them. 
% 尽管绝大多数的大河流域都在快速发展的同时极大提高了管理水资源的能力和用水的效率，但大部分研究仍悲观的指出淡水利用已经临近系统崩溃的行星边界。
Although most large river basins improved water management and efficiency along with development, most studies still pessimistically point out that freshwater use is reaching planetary boundaries where human-water systems may collapse.
% 总的来说，这可能有两点主要原因。
Overall, there are probably two main reasons.
% 首先，效率悖论
Firstly, significant improvement in agricultural irrigation efficiency is usually accompanied by re-expansion in irrigated area, resulting in a usually unabated trend of water resources stress which is known as paradox of efficiency 
\cite{graftonParadoxIrrigationEfficiency2018}. 
% 其次，以水-社会水循环为主导的治理机制下，水资源分配或提供结构复杂，可能导致水资源利用不灵活，破坏流域的恢复能力
Secondly, complicated structure of water allocation or provision under a governance regime dominated by hydro-social water cycle may lead the water governance more inflexible and damage to resilience of the basin
\cite{qinFlexibilityIntensityGlobal2019}.
% 这时，我们需要相应的全面策略应对这种治理挑战，因为挑战的核心要素超出了任何一个参与的控制。
At this point, we need corresponding comprehensive strategies to address the governance challenges, because the heart factors of are beyond the control of any related actor. 
% 基于对治理体制转型对理解，我们可以创造有利条件以应对挑战，并保持流域社会-生态系统对弹性，以实现可持续发展。
Based on the understanding of governance regime transition, we can create favourable conditions for meeting the challenges and maintaining the resilience of the basin's socio-ecosystem, towards sustainability.
% 总的来说，这些都有助于指导流域迈向可持续性。
% Taken together, these have helped guide the basin towards sustainability.
